HW #4: Analyze real-world emissions data RESUBMISSION

### 2022-12-10 HW2/HW2.Rmd
update hw2 and 4 for resubmission

---
title: "HW 2: Energy Demand and CO2 Emissions"
author: "Hayden Atchley"
date: "`r Sys.Date()`"
output:
  pdf_document:
    latex_engine: xelatex
mainfont: Gentium Book Basic
---

@@

## 1.1
The average fuel economy is

@@

@@

enginepower <- sum(tp$`Engine Power (kW)`)
```

@@

## 2.7
Low-sulfur diesel has an energy content of 128,488 Btu/gal according to the AFDC. This is equivalent to `r (energy <- 37.656)` kWh/gal. Assuming an engine efficiency of `r (eff <- 0.3)`, the total fuel needed for this drive cycle is $F = \frac{`r (enginepower) %>% round()`[\text{kWh}]/`r eff`}{`r energy %>% round(1)`[\text{kWh/gal}]} = `r (fuel1 <- enginepower/energy/eff) %>% round()`\ \text{gal}$. The total distance in this drive cycle is `r (totdist <- sum(tp$dist, na.rm = TRUE)) %>% round()` meters or `r (miles <- (totdist * .0006213712)) %>% round(1)` miles, giving an overall fuel economy of `r (miles/fuel1) %>% round(2)` mpg, and a fuel consumption of `r (fuel1/miles*1000) %>% round()` gallons per 1000 miles.

@@

## 2.9

>>>>

---
title: "HW 2: Energy Demand and CO2 Emissions RESUBMISSION"
subtitle: "See 1.1, 2.7, 2.9"
author: "Hayden Atchley"
date: "`r Sys.Date()`"
output:
  pdf_document:
    latex_engine: xelatex
mainfont: Gentium Book Basic
---

@@

## 1.1
Previously, I erroneously added the fuel economies together rather than totaling the distance and the fuel and dividing. The correct average fuel economy is

@@

		enginepower = `Engine Power (kW)`*t/3600,

@@

enginepower <- sum(tp$enginepower, na.rm = TRUE)
```

@@

## 2.7
Previously I used the tractive power rather than the engine power. This has been fixed.

Low-sulfur diesel has an energy content of 128,488 Btu/gal according to the AFDC. This is equivalent to `r (energy <- 37.656)` kWh/gal. Assuming an engine efficiency of `r (eff <- 0.3)`, the total fuel needed for this drive cycle is $F = \frac{`r (enginepower) %>% round()`[\text{kWh}]/`r eff`}{`r energy %>% round(1)`[\text{kWh/gal}]} = `r (fuel1 <- enginepower/energy/eff) %>% round()`\ \text{gal}$. The total distance in this drive cycle is `r (totdist <- sum(tp$dist, na.rm = TRUE)) %>% round()` meters or `r (miles <- (totdist * .0006213712)) %>% round(1)` miles, giving an overall fuel economy of `r (miles/fuel1) %>% round(2)` mpg, and a fuel consumption of `r (fuel1/miles*1000) %>% round()` gallons per 1000 miles.

@@

## 2.9
Previously I had not written a response to this question.

### 2022-12-10 HW4/HW4.Rmd
update hw2 and 4 for resubmission

---
title: "HW #4: Analyze real-world emissions data"
author: Hayden Atchley
date: "`r Sys.Date()`"
mainfont: Gentium Book Basic
output:
  bookdown::pdf_document2:
    toc: false
    number_sections: false
---

@@

@@

@@

However, the mean emissions at each _location_ is in fact random and independent, as now the effect these previously-mentioned variables can be captured, that is, the effect on the _location_ means. We therefore take the mean emissions at each location:
```{r}
site %>%
	`names<-`(c("Location", "Mean Emissions")) %>% 
	kbl(digits = 1, booktabs = TRUE) %>% 
	kable_styling(latex_options = "HOLD_position")
```
and can now find the mean of _these_ values to estimate the mean emission rate for all of Utah County (with 95% confidence interval):

>>>>

---
title: "HW #4: Analyze real-world emissions data RESUBMISSION"
subtitle: "See 3 & 6"
author: Hayden Atchley
date: "`r Sys.Date()`"
mainfont: Gentium Book Basic
output:
  bookdown::pdf_document2:
    toc: false
    number_sections: false
---

@@

**Previously I didn't answer this question**

@@

**Previously I used _all_ samples as if they were independent rather than the means at each location.**

@@

However, the mean emissions at each _location_ is in fact random and independent, as now the effect these previously-mentioned variables can be captured, that is, the effect on the _location_ means. We therefore take the mean emissions at each location:
```{r}
site %>%
	`names<-`(c("Location", "Mean Emissions")) %>% 
	kbl(digits = 1, booktabs = TRUE, linesep = "") %>% 
	kable_styling(latex_options = "HOLD_position")
```
and can now find the mean of _these_ values to estimate the mean emission rate for all of Utah County (with 95% confidence interval):
